Report

### 2021-06-14 Rmd/report.Rmd
Add more sanity checks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		ggplot2.discrete.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.discrete.colour = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.continuous.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.continuous.colour = RColorBrewer::brewer.pal(6, name = "Dark2")
)

@@

# load data
gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant)
fit <- readRDS(here("Results", "fit.rds"))
fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(valid_status = case_when(
		!valid_vocab ~ "Invalid vocabulary",
		!valid_gaze ~ "Invalid gaze",
		!valid_other ~ "Other",
		!valid_participant ~ "Invalid participant",
		TRUE ~ "Valid"
	)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1),
		axis.text.y = element_text(size = 8),
		axis.title.y = element_blank()
	)
```

@@

## Target fixations {.tabset .tab-pills}

### Aggregated by trial

For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen. Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated). Some participants were longitudinal. Scores form longitudinal participant  are indicated by grey lines linking data points from the same participant.

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	count(age_group, lp)

gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(aes(trial_type, prop, colour = trial_type, fill = trial_type),
				position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(trial_type, prop, colour = trial_type, fill = trial_type,
					 group = interaction(age_group, trial_type)),
				 width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75),
				 colour = "black", fill = "white") +
	geom_text(data = sample_size,
			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

### Growth curve analysis {.tabset .tab-pills}

#### Model details

@@

#### Fixed effects

@@

gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
main_effects
```

#### Random effects

@@

##### {-}

@@

#### Marginal means {.tabset .tab-pills}

##### Overall

@@

##### By vocabulary size

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size <= median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size <= median(.$vocab_size)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size > median(.$vocab_size)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By location

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### {-}

#### 21 month-old monolinguals

@@

gtsave(data = main_effects, filename = "main_effects_21_mon.png", path = here("Figures"))
main_effects

@@

@@

# Appendix {.tabset .tab-pills}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		ggplot2.discrete.fill = ggthemes::colorblind_pal()(8),
		ggplot2.discrete.colour = ggthemes::colorblind_pal()(8),
		ggplot2.continuous.fill = ggthemes::colorblind_pal()(8),
		ggplot2.continuous.colour = ggthemes::colorblind_pal()(8)
)

@@

# load data
gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant)
fit <- readRDS(here("Results", "fit.rds"))
fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(valid_status = case_when(
		!valid_vocab ~ "Invalid vocabulary",
		!valid_gaze ~ "Invalid gaze",
		!valid_other ~ "Other",
		!valid_participant ~ "Invalid participant",
		TRUE ~ "Valid"
	)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

## Growth curve analysis {.tabset .tab-pills}

### Model details

@@

### Fixed effects

@@

main_effects
```

### Random effects

@@

@@

### Marginal means {.tabset .tab-pills}

#### Overall

@@

#### By vocabulary size

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size_center <= median(.$vocab_size_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_center <= median(.$vocab_size_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_center > median(.$vocab_size_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

#### By location

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

### 21 month-old monolinguals {.tabset .tab-pills}

#### All data

@@

main_effects

@@

#### Location

```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, location)

augment(fit_21_mon_location) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  	colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_location) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, location, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) &
	ggsave(here("Figures", "emmeans_21_mon_location.png"))
```

#### Vocabulary (median split)

```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sample_size <- participants %>% 
	drop_na(vocab_size_center) %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	mutate(vocab_cat = ifelse(vocab_size_center > median(participants$vocab_size_center, na.rm = TRUE), "Above median", "Below median")) %>% 
	count(age_group, vocab_cat, lp)

augment(fit_21_mon_vocab) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
		geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, vocab_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) &
	ggsave(here("Figures", "emmeans_21_mon_vocab.png"))
```

#### Vocabulary (balanced)

```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocab (balanced)
sample_size <- participants %>%
	drop_na(vocab_size) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	count(location)

augment(fit_21_mon_vocab_pct) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  	colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_pct) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, location, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) &
	ggsave(here("Figures", "emmeans_21_mon_vocab_pct.png"))
```

@@

# Appendix
